Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-06-17 ms.tex
last referee comments: archival imaging

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.
\change{We then run an MCMC \btmtodo{still a chain?} using \texttt{MULTINEST} \citep{Feroz09},
an implementation of a multimodal nested sampling algorithm,}
for each host star conditioned on the observed
photometric properties as presented in Table 1.
We include a prior on stellar metallicity representative of the observed metallicities
of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and a Salpeter-slope
prior on mass up to the maximum mass available in the model grids of $3.7$ $M_\odot$.

\change{During the sampling process, we fit for galactic
extinction as one of our physical parameters.
For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
along that line of sight from the NED \btmtodo{acronym}, which reports the 
\citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
COBE/DIRBE and IRAS/ISSA. 
The NED database returns the extinction in all relevant bandpasses except those used by
WISE, assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}.
We include the WISE bandpasses by applying the relative extinction values between 
SDSS, 2MASS, and WISE calculated by \citep{Davenport14}.
In each step of our fitting process, we draw an $A_V$, calculate the expected extinction
in all bandpasses $A_X$, and then measure the likelihood of our model stellar fit to the 
observed apparent magnitudes.
We apply a uniform prior ranging from zero to the obtained maximum extinction value and
marginalize over extinction in our final determination of stellar parameters. }

@@

%%%
%%%  I haven't actually done this... perhaps I can do it in response to
%%%  referee if they ask for it...
%%%
% One system, EPIC 201828749, is known to be a binary through AO imaging
% as discussed in \textsection\ref{sec:AO}.
% In this case, we do account for the dilution induced by the companion.
% From our relative $JHK$ photometry of the two stars, we infer an expected flux
% ratio between the two stars in the \kep\ bandpass, inflating the transit depth
% by this factor to account for the dilution.
% We marginalize  \dfmtodo{More text...}

@@

We include this extra analysis step for EPIC 201912552, considering
the additional follow-up this target may warrant.
We download data from the POSS I and II surveys, which imaged
EPIC 201912552 in 1955 and 1989, respectively.
This star has a proper motion of $-74 \pm 2$ mas yr$^{-1}$ in right ascension
 and $-122 \pm 4$ mas yr$^{-1}$ in declination, so it has moved by $8\farcs35$
since the POSS I data were collected.
As shown in Figure~\ref{fig:archival}, we do not detect any targets at the
present-day location of EPIC 201912552 in either of the POSS surveys.

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth, trim=0 6.30cm 0 6.30cm, clip=true]{f5}}
\caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background
object directly behind the present day location of the target (red circle) that could be missed
by the AO observations, while modern SDSS imaging can rule out wide companions
that may have been missed at wide separations, beyond the AO field of view.
All subplots are on the same scale.}
\label{fig:archival}
\end{figure*}

@@

\btmtodo{NED?}

>>>>

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.
\change{We then infer the stellar parameters using \texttt{MULTINEST} \citep{Feroz09},
an implementation of a multimodal nested sampling algorithm,}
for each host star conditioned on the observed
photometric properties as presented in Table 1.
We include a prior on stellar metallicity representative of the observed metallicities
of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and a Salpeter-slope
prior on mass up to the maximum mass available in the model grids of $3.7$ $M_\odot$.

\change{During the sampling process, we fit for galactic
extinction as one of our physical parameters.
For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
along that line of sight from the NASA/IPAC Extragalactic Database (NED), which reports the 
\citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
COBE/DIRBE and IRAS/ISSA. 
The NED database returns the extinction in all relevant bandpasses except those used by
WISE, assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}.
We include the WISE bandpasses by applying the relative extinction values between 
SDSS, 2MASS, and WISE calculated by \citep{Davenport14}.
In each step of our fitting process, we draw an $A_V$, calculate the expected extinction
in all bandpasses $A_X$, and then measure the likelihood of our model stellar fit to the 
observed apparent magnitudes.
We apply a uniform prior ranging from zero to the obtained maximum extinction value and
marginalize over extinction in our final determination of stellar parameters. }

@@

@@

\change{Five of the stars in our sample have proper motions larger than 50 mas
yr${-1}$, so they have moved across the sky by $\gtrsim 2\farcs5$ since
they were imaged during the first Palomar Observatory Sky Survey (POSS) in the
1950s. 
To rule out background companions, we download data from the POSS I
and II surveys, which imaged these targets in 1952-1955 and 1989-1998,
respectively.
We also download data from the Sloan Digital Sky Survey, which imaged
these fields between 2000 and 2009.
As shown in Figure~\ref{fig:archival}, we do not detect any background
targets at the present-day location of any of these stars in any of these
images.
}

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.65\textwidth]{f5}}
\caption{Archival maging for the five highest proper motion targets in our sample. 
In all cases, there are no background
objects directly behind the present day location of the target (red circle) that could be missed
by the AO observations. Modern SDSS imaging can also rule out wide companions
that may have been missed at wide separations, beyond the AO field of view, such as the
companion which can be seen in the images of EPIC 201577035.
All figures are aligned such that north is up and east to the left.
All subplots are on the same scale.}
\label{fig:archival}
\end{figure*}

@@

This research has made use of the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration.
